Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/intro.tex

In this paper we focus on the sensitivity to time discretization of DRL
approaches, such as what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$.
In principle, decreasing time discretization, or equivalently
shortening reaction time, should only improve agent performance.
Robustness to time discretization is especially relevant in
\emph{near-continuous} environments, which includes most continuous
control environments, robotics, and many video games.  
We focus on
near-continuous time because this leads to a clear framework, but the
approach below would be relevant in any setting in which the advantage of
any single individual action is small compared to the total return.%, for instance, long time horizon problems.

@@

>>>>

In this paper we focus on the sensitivity to time discretization of DRL
approaches, such as what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$.
In principle, decreasing time discretization, or equivalently
shortening reaction time, should only improve agent performance.
Robustness to time discretization is especially relevant in
\emph{near-continuous} environments, which includes most continuous
control environments, robotics, and many video games.

@@

We focus on near-continuous time because this leads to a clear framework,
but our observations make sense in any setting in which the value
results from a taking a large number of small individual actions. Our
results suggest naive $Q$-learning will fail in such settings without a
delicate balance of hyperparameter scalings.
%the
%advantage of any single individual action is small compared to the total
%return.%, for instance, long time horizon problems.
